Sparse Function-space Representation \\ of Neural Networks

### 2023-05-13 paper/main.tex
commit start of rewrite 2

%A Gaussian procss characterizes a distribution over functions in terms of the first two moments. The key quantity of 
%A Gaussian process is the prior covariance function (or kernel function) $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$. We aim to find a kernel based on the neural network to build the Gaussian process posterior. 
A GP is fully characterized by a mean $\mu(\cdot)$ and covariance function $\kappa(\cdot,\cdot)$ (kernel).
If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx') = \delta^{-1} \phi(\vx) \phi^\T(\vx')$ (see Ch.~XXX in \cite{rasmussen2006gaussian} for details).\todo{this part needs to be rewritten, starts talking about a general function parameterisation and then jumps directly to the neural network} 
%=======
\subsection{Neural Network to GP Prior} 
\label{sec:nn2gp}
%
A common approach to find a distribution over $q(\vw)$ is to perform a Laplace-GGN approximation. The approximation can be seen as taking the Laplace approximation of \cref{eq-empirical-risk} and approximating the   Hessian of $\ell(f_\weights(\mathbf{x}_{i}), \mathbf{y}_i)$ with the Generalized Gauss Newton(GGN) approximation. \citet{immerImprovingPredictionsBayesian2021} proposed to make the following linear approximation
$f^{\textrm{lin.}}_{\vw^*}(\vx; \vw) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} \, (\vw - \vw^*)$ of the neural network, with Jacobian $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$. The idea

>>>>

%A Gaussian procss characterizes a distribution over functions in terms of the first two moments. The key quantity of 
%A Gaussian process is the prior covariance function (or kernel function) $\kappa(\vx,\vx')$, where $\vx, \vx'$ are input vectors in $\R^{\mathrm{D}}$. We aim to find a kernel based on the neural network to build the Gaussian process posterior. 
A GP is fully characterized by a mean $\mu(\cdot)$ and covariance function $\kappa(\cdot,\cdot)$ (kernel).
If we had the following function parameterization $g(\vx) = \phi(\vx)^\top \vw$ where $\phi(\vx)$ is a feature map, we can convert from weight space prior to function space prior giving the following kernel $\kappa(\vx, \vx') = \delta^{-1} \phi(\vx) \phi^\T(\vx')$ (see Ch.~XXX in \cite{rasmussen2006gaussian} for details).\todo{this part needs to be rewritten, starts talking about a general function parameterisation and then jumps directly to the neural network} 
%=======
\subsection{Neural Network to GP Prior} 
\label{sec:nn2gp}
%
Given an approximate posterior $q(\vw)$  \citet{immerImprovingPredictionsBayesian2021} proposed to make the following linear approximation
$f^{\textrm{lin.}}_{\vw^*}(\vx; \vw) = f_{\vw^*}(\vx) + \Jac{\weights^*}{\mathbf{x}} \, (\vw - \vw^*)$ of the neural network, with Jacobian $\Jac{\weights}{\mathbf{x}} \coloneqq \nabla_\weights f(\mathbf{x})^\top \in \R^{C \times P}$. The approximation can be used with any approximate inference technique but in the paper they focus on the Laplace-GNN. They find that the linear approximation helps to improve predictions by correcting the approximate posterior when sampled through a non-Gaussian likelihoods.
